### 2021-07-29 doc/thesis/chapters/results.tex
figure

@@

In the comparison against the Matlab model, the HLS variant achieves a very exact match of the output signal.
However, the VHDL implementation differs by a certain amount.
There seems to be an issue in the signal separation between the left and right audio channels.
This is visible in the analysis of the audio signal, as shown is Fig. \ref{fig:audio_output_compare_ips_vs_matlab}.
The signal strength of the left channel in the upper diagram is weaker than expected, while the right channel in the lower diagram is stronger.
This imbalance can also be observed by listening to the audio output via speakers.\\

@@

%TODO: find a good time-range for this picture and format it correctly
\includepicture [1.0] [0] {Comparison of the IPs audio signals against the Matlab model. The HLS variant matches the model, while the VHDL output diverts by a certain amount.} {audio_output_compare_ips_vs_matlab} {img/matlab/audio_output_compare_ips_vs_matlab}

@@

%TODO: find a good time-range for this picture and format it correctly
\includepicture [1.0] [0] [H] {Comparison of the audio signal in simulation testbench and hardware.} {audio_output_compare_tb_vs_hw} {img/matlab/audio_output_compare_tb_vs_hw}

>>>>

\includepicture [1.0] [0] {Comparison of the IP audio output signals, in simulation and hardware, against the Matlab model. The HLS variant matches the model, while the VHDL output diverts by a certain amount. Also, VHDL differs between simulation- and hardware results.} {audio_output_compare_tb_vs_hw} {img/matlab/audio_output_compare_tb_vs_hw}

@@

In the comparison against the Matlab model, the HLS variant achieves a very exact match of the output signal.
However, the VHDL implementation differs by a certain amount.
There seems to be an issue in the signal separation between the left and right audio channels.
This is visible in the analysis of the audio signal, as shown is Fig. \ref{fig:audio_output_compare_tb_vs_hw}.
The signal strength of the left channel in the upper diagram is weaker than expected, while the right channel in the lower diagram is stronger.
This imbalance can also be observed by listening to the audio output via speakers.\\

@@

%\includepicture [1.0] [0] {Comparison of the IP audio output signals against the Matlab model. The HLS variant matches the model, while the VHDL output diverts by a certain amount.} {audio_output_compare_ips_vs_matlab} {img/matlab/audio_output_compare_ips_vs_matlab}

@@
